Consensus cell types across osteosarcoma samples

### 2025-02-11 analyses/cell-type-consensus/exploratory-notebooks/03-osteosarcoma-consensus-celltypes.Rmd
move plotting functions to utils

## Functions

```{r}
# barchart with or without faceting
# each bar is a stacked barchart using the fill_color
# faceting is only done if a facet_variable is provided
stacked_barchart <- function(
    df, 
    fill_column,
    celltype_colors, # named vector where names match the values in fill_column
    facet_variable = NULL
){

  barchart <- ggplot(df) + 
    aes(
      x = library_id, 
      y = percent_cells_annotation, 
      fill = !!sym(fill_column)
    ) +
    geom_col() + 
    scale_y_continuous(expand = c(0,0)) +
    scale_fill_manual(values = celltype_colors) +
    theme(axis.text.x = element_blank()) +
    labs(
      fill= "cell type"
    )

  if(!is.null(facet_variable)){
    barchart <- barchart +
      facet_wrap(vars(!!sym(facet_variable)), scales ="free_x")
  }

  return(barchart)
}

# sina plot looking at immune percentage on the y-axis 
sina_plot <- function(df, plot_column){

  ggplot(df, aes(x = !!sym(plot_column), y = percent_immune)) +
    ggforce::geom_sina() +
    stat_summary(fun.y=median, geom="crossbar" , color = "red", linewidth = 0.2) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
          plot.margin = margin(10,10,10,10)) +
    labs(
      x = "", 
      y = "Percent of cells annotated as Immune",
      title = plot_column
    )

}
```

@@

```{r}
# source summarize_celltypes() function
setup_functions <- file.path(module_base, "exploratory-notebooks", "utils", "setup-functions.R")
source(setup_functions)
```

>>>>

@@

```{r}
# source summarize_celltypes() function
setup_functions <- file.path(module_base, "exploratory-notebooks", "utils", "setup-functions.R")
source(setup_functions)

# source stacked_barchart() and sina_plot() functions
plotting_functions <- file.path(module_base, "exploratory-notebooks", "utils", "plotting-functions.R")
source(plotting_functions)
```
